NDNS multilevel LCA CW2CB2 or CW2CB3

### 2018-07-24 paper/Chapters/Chapter2.tex
strata weighting etc. added

To produce a sequence of discrete responses about the carbohydrate intake we are interested, we calculated the energy consumption per hour for each participant. The percentage of energy that contributed by carbohydrate within each hour were calculated for every every participant, each single day. Since we planed to apply latent class analysis (LCA) in the current study, in which the observed indicators for latent classes must be categorical, we then dichotomised the responses according to the carbohydrate contribution to the energy intake at cut-off value of 50\%, i.e. if within an hour if there is any energy intake occured, carbohydrate consumption was categorised into whether it's energy contribution was higher or equal to 50\% of total energy. Consequently, for each day of the recording, there were 24 data points generated by the dairy, each data point included one of the following responses:

@@

The response rates for completion of the food diary (three or four days) were 56\%, 53\%, 53\%, for years 1 to 4 combined, 5 to 6 combined and 7 to 8 combined, respectively. A total of 6,155 adults aged 19 years and over were kept in our analysis. 
\vspace{-1.2cm}

@@

@@

>>>>

To produce a sequence of discrete responses about the carbohydrate intake we are interested, we calculated the energy consumption per hour for each participant. The percentage of energy that contributed by carbohydrate within each hour were calculated for every every participant, each single day. Since we planed to apply latent class analysis (LCA) in the current study, in which the observed indicators for latent classes must be categorical, we then dichotomised the responses according to the carbohydrate contribution to the energy intake at cut-off value of 50\%, i.e. if within an hour there is any energy intake occured, carbohydrate consumption was categorised into whether it's energy contribution was lower or higher/equal to 50\% of total energy intake within that hour. Consequently, for each day of the recording, there were 24 data points generated by the dairy, each data point included one of the following responses:

@@

The response rates for completion of the food diary (three or four days) were 56\%, 53\%, 53\%, for years 1 to 4, 5 to 6, and 7 to 8, respectively. A total of 6,155 adults aged 19 years and over were kept in our analysis. 
\vspace{-0.6cm}

@@

Two steps of weighting system are designed in the NDNS RP to assure that the combined sample will be representative of the UK population:

\begin{enumerate}
	\item An overall selection weight, which is the product of the address, dwelling unit, catering(household) unit, and individual selection weights, was generated to correct for the unequal selection probabilities. These weights are the inverse of the selection probabilities at each level of the random sampling process and they can be used to compensate for differences in the chance of selection of an individual.
	\item An iterative procedure was used to adjust the selection weights until the distribution of the weighted sample matched that of the population for age-group, sex and geographical region. Population distributions were taken from the mid-year population estimates \parencite{OfficeofNationalStat}. 
\end{enumerate}

Another set of weights were generated to correct for differential non-response (either due to refusal or inability) to giving a blood sample. Response to the blood sample in adults were 51\%, 57\%, and 50\% for years 1 to 4, 5 to 6, and 7 to 8, respectively. In creating the blood sample weight, a logistic regression was used by the NDNS RP study team to model the relationship between response to giving blood sample and a set of predictor variables (socio-demographic, participant and catering/household unit characteristics). The model generated a predicted probability for each participant, which is the probability would provide blood sample, given the characteristics of the individual and the household unit. Participants with characteristics associated with non-response were under-represented in the blood sample and therefore receive a low predicted probability. The inverse of these predicted probablities were used as a set of non-response weights so that participants with a low predicted probability got a larger weight, increasing their representation in the sample. Then the blood sample weights were re-scaled so that the sum of the weights equalled the number of participants who had a nurse visit. The final blood weights should therefore make the blood sample participants representative of all eligible persons in the population.

Further details of the weighting system developed by the NDNS RP are described in the Appendix B of the reports published by Public Health England (PHE) \parencite{bates2014national,roberts2018national}.

@@

\section{Association between latent classes and other variables}\vspace{-0.3cm}
